Software Citation Principles

### 2016-02-25 sc-principles/software-citation-principles.tex
spell out SSI at least once

The Force11 Software Citation Working Group~\cite{f11scwg} was created in April 2015.
It gathered members, and then in June 2015 began studying this, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and draft this resulting document,
which will be presented and discussed at the Force2016 Conference \cite{force2016}
in April 2016.  We expect that
this discussion may lead to a second, final version, and we also
plan to have a follow-on working group that will interact with stakeholders to ensure that
these principles impact the scientific process.

@@

Some of the most actionable work has come from the SSI in the form of blog posts written by their community fellows:

>>>>

The Force11 Software Citation Working Group~\cite{f11scwg} was created in April 2015.
It gathered members, and then in June 2015 began studying this, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and draft this resulting document,
which will be presented and discussed at the Force2016 Conference \cite{force2016}
in April 2016.  We expect that
this discussion may lead to a second, final version, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the scientific process.

@@

Some of the most actionable work has come from the NSF Software Infrastructure for Sustained Innovation (SSI) program in the form of blog posts written by their community fellows:
